### 2016-05-06 ch02-qlogms/excitation-design.tex
Small stuff
Fix $\Alpha$ -> $\alpha$

\chapter{Design of Excitation Signals}
\label{sec:excitation}
\def\thisDir{ch02-qlogms}
\tikzsetfigurename{ch02fig}
\myEpigraph{A common mistake that people make when trying to design something completely foolproof is to underestimate the ingenuity of complete fools.}{Douglas Adams}{Mostly Harmless}
\researchBasedOn{Larsson2012SYSID, Geerardyn2012IMTC, Geerardyn2013TIM, }

@@

  \subsection{Selection of the Frequency Grid Spacing $\Alpha$}
  Since the damping influences the $3\unit{dB}$ bandwidths, this will become important when one has to determine the grid spacing $\alpha$.
  To deal with this, we introduce the normalized frequency ratio
  \begin{equation}
    \tilde{\alpha} = \frac{\alpha - 1}
                          {\damping}
                   \propto \frac{\omega_{k+1} - \omega_k}
                                {\wdB}
                           \cdot
                           \frac{\wn}{\omega_k}
    \text{.}
    \label{eq:excitation:normAlpha} 
  \end{equation}
  This normalized frequency ratio can be interpreted as a measure of the grid resolution, relative to the $3\unit{dB}$ bandwidth of the second order system.
  The grid resolution in a (quasi-) log grid is $\left( \alpha - 1\right)\omega_k$ while the system bandwidth is approximately $2\damping\wn$.
  Around the resonance, $\omega_k \approx \wn$, such that the last fraction in \eqref{eq:excitation:normAlpha} can safely be neglected.

>>>>

\chapter{Design of Excitation Signals}
\label{sec:excitation}
\def\thisDir{ch02-qlogms}
\tikzsetfigurename{ch02fig}
\myEpigraph{A common mistake that people make when trying to design something completely foolproof is to underestimate the ingenuity of complete fools.}{Douglas Adams}{Mostly Harmless}
\researchBasedOn{Larsson2012SYSID, Geerardyn2012IMTC, Geerardyn2013TIM}

@@

  \subsection{Selection of the Frequency Grid Spacing $\alpha$}
  Since the damping influences the $3\unit{dB}$ bandwidths, this will become important when one has to determine the grid spacing $\alpha$.
  To deal with this, we introduce the normalized frequency ratio
  \begin{equation}
    \tilde{\alpha} = \frac{\alpha - 1}
                          {\damping}
                   \propto \frac{\omega_{k+1} - \omega_k}
                                {\wdB}
                           \cdot
                           \frac{\wn}{\omega_k}
    \text{.}
    \label{eq:excitation:normAlpha} 
  \end{equation}
  This normalized frequency ratio can be interpreted as a measure of the grid resolution, relative to the $3\unit{dB}$ bandwidth of the second order system.
  The grid resolution in a (quasi-) log grid is $\left( \alpha - 1\right)\omega_k$ while the system bandwidth is approximately $2\damping\wn$.
  Around the resonance, $\omega_k \approx \wn$, such that the last fraction in \eqref{eq:excitation:normAlpha} can safely be neglected.
